---
title: "Empirical power analysis for three-player variant"
author: "Matt Jaquiery (matt.jaquiery@psy.ox.ac.uk)"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '3'
    # css: ../src/writeUp.css
    # includes:
      # after_body: ../src/toc_menu.html
editor_options:
  chunk_output_type: inline
---

October 2020

[Script run `r Sys.time()`]

# Feelings of Responsibility by Receivership of Reward
## Marwa El Zein and Matt Jaquiery

On the basis of several pilot experiments, we have arrived at a design with one participant and two simulated players making decisions on each trial, and with the participant rating the responsibility of every player on all trials.
The most subtle effect of interest to us is the three-way interaction between Outcome Valence, Outcome Recipient, and whether the rated player is the participant.
We therefore run simulations (using participants' actual data as a template) to explore how many participants we might need to detect an interaction effect of d = .3 against a background of the other effects being sized as they were for the real participants.

### Structure

The task structure occurs in sets of 20 trials (1:1 ratios for minority/majority and no/reward, and 2:3 ratio for participant/other rewarded). There are three of these sets in a study. Below we use an example simulation of one study of one participant to demonstrate the trial structure:

```{r echo=T}
library(tidyverse)

source("generate-data.R")
betas <- list('8' = .3)  # 3-way interaction is the 8th parameter
n <- 50
path_adjust <- '../'

# generate-data.R exports this function
generateData.full(n, betas, path_to_root_dir = path_adjust)

```

### Power analysis

First we define a function which will run the simulations and perform ANOVA on the results. 

```{r echo=T}

#' @param r repetitions to run
#' @param n number of participants to simulate in each repetition
#' @param betas betas to override in participant data
#' @param printTo location to save output if desired
sim <- function(r, betas, betaSDs = NULL, n = 50, printTo = NULL) {
  require(ez)
  require(purrr)
  require(magrittr)
  require(dplyr)
  require(tidyr) # required by generateData.full
  require(tibble) # required by generateData.full
  require(stringr) # required by generateData.full
  
  aovs <- tibble(
    repetition = r,
    beta8 = betas['8'],
    beta8_sd = betaSDs['8'],
    n = n,
    d = map(1, ~generateData.full(n, betas, betaSDs, path_to_root_dir = path_adjust))
  )
  
  suppressWarnings(
    aovs <- aovs %>%
      mutate(
        aov = map(
          d, 
          ~ezANOVA(
            data = .,
            dv = responsibility_rating,
            wid = simID,
            within = .(
              outcome, 
              rated_gets_outcome, 
              is_participant
            )
          )
        )
      )
  )
  
  # fetch unique contribution of the outcome:pGetsOutcome interaction in anova and anovaBF
  f <- function(x) 
    x$ANOVA %>% 
    filter(Effect == 'outcome:rated_gets_outcome:is_participant') %>% 
    .$p
  aovs <- aovs %>%
    mutate(p = map_dbl(aov, f))
  
  out <- aovs %>% select(-d, -aov)
  
  if (!is.null(printTo)) 
    write.table(
      out, 
      printTo, 
      sep = ",", 
      append = T, 
      col.names = F, 
      row.names = F
    )
  
  out
}

```

Then we set that to run in parallel for some number of repetitions.

```{r echo=T}
newData <- F
if (newData) {
  library(parallel)
  
  reps <- 100
  params <- crossing(
    repetition = 1:reps,
    n = c(5, 25, 50, 150, 500, 5000),
    es = c(0, .05, .15, .25, .5)
  )
  
  timeStart <- Sys.time()
  
  cl <- makeCluster(detectCores() - 4)
  
  clusterExport(cl, c("sim", "reps", "generateData.full", "path_adjust"))
  
  aovs <- parApply(cl, params, 1, FUN = function(r) {
    sim(r = r['repetition'], n = r['n'], betas = list('8' = r['es']))
  })
  
  stopCluster(cl)
  
  timeEnd <- Sys.time()
  
  print(paste0(
    "Data generation complete. Generated ",
    length(aovs), " ANOVAs in ",
    round(difftime(timeEnd, timeStart, units = "secs"), 2), "s."
  ))
  
  # join list to table structure
  aovs <- tibble(id = 1:length(aovs)) %>%
    mutate(d = map(id, ~aovs[[.]])) %>%
    unnest(cols = d)
  
  # save the list for later because it takes hours!
  write.table(
    aovs, 
    'tmp-data/three-player-aovs.csv', 
    sep = ",", 
    append = F, 
    col.names = T, 
    row.names = F
  )
} else {
  aovs <- read.csv('tmp-data/three-player-aovs.csv')
}

```

Finally we print some results

```{r}

alpha = .05

aovs %>% 
  group_by(beta8, n) %>%
  summarise(pSig = mean(p < alpha), .groups = 'drop') %>%
  mutate(across(-pSig, factor)) %>%
  ggplot(aes(x = n, y = beta8, fill = pSig)) +
  geom_tile() +
  geom_text(aes(label = round(pSig, 3)), colour = "white") +
  scale_fill_continuous(name = "P(p < .05)", limits = c(0, 1)) +
  labs(
    title = "Heatmap of the probability of a significant result",
    y = "3-way interaction effect size (d)",
    x = "Number of participants"
  )

aovs %>% 
  select(p, beta8, n) %>%
  mutate(across(-p, factor)) %>%
  ggplot(aes(x = p, y = beta8)) +
  geom_vline(xintercept = .05, linetype = 'dashed') +
  ggridges::geom_density_ridges() +
  facet_wrap(~n)

```

#### Zooming in on the region of interest

```{r echo=T}
newData <- F
if (newData) {
  library(parallel)
  
  reps <- 1000
  params <- crossing(
    repetition = 1:reps,
    n = c(150, 200, 250, 500),
    es = c(-.14, -.07, .07, .14),
    es_sd = .44 # empirically determined
  )
  
  timeStart <- Sys.time()
  
  cl <- makeCluster(detectCores() - 4)
  
  clusterExport(cl, c("sim", "reps", "generateData.full", "generateData.exclude", "path_adjust"))
  
  aovs <- parApply(cl, params, 1, FUN = function(r) {
    sim(
      r = r['repetition'], 
      n = r['n'], 
      betas = list('8' = r['es']),
      betaSDs = list('8' = r['es_sd'])
    )
  })
  
  stopCluster(cl)
  
  timeEnd <- Sys.time()
  
  print(paste0(
    "Data generation complete. Generated ",
    length(aovs), " ANOVAs in ",
    round(difftime(timeEnd, timeStart, units = "secs"), 2), "s."
  ))
  
  # join list to table structure
  aovs <- tibble(id = 1:length(aovs)) %>%
    mutate(d = map(id, ~aovs[[.]])) %>%
    unnest(cols = d)
  
  # save the list for later because it takes hours!
  aovs %>%
    mutate(across(is.list, unlist)) %>%
    write.table(
      'tmp-data/three-player-aovs-zoom.csv', 
      sep = ",", 
      append = F, 
      col.names = T, 
      row.names = F
    )
} else {
  aovs <- read.csv('tmp-data/three-player-aovs-zoom.csv')
}

```

```{r}

alpha = .05

aovs %>% 
  mutate(beta8 = unlist(beta8)) %>%
  group_by(beta8, n) %>%
  summarise(pSig = mean(p < alpha), .groups = 'drop') %>%
  mutate(across(-pSig, factor)) %>%
  ggplot(aes(x = n, y = beta8, fill = pSig)) +
  geom_tile() +
  geom_text(aes(label = round(pSig, 3)), colour = "white") +
  scale_fill_continuous(name = "P(p < .05)", limits = c(0, 1)) +
  labs(
    title = "Heatmap of the probability of a significant result",
    y = "3-way interaction effect size (d)",
    x = "Number of participants"
  )

aovs %>% 
  mutate(beta8 = unlist(beta8)) %>%
  select(p, beta8, n) %>%
  mutate(across(-p, factor)) %>%
  ggplot(aes(x = p, y = beta8)) +
  geom_vline(xintercept = .05, linetype = 'dashed') +
  ggridges::geom_density_ridges() +
  facet_wrap(~n)

```

## Technical details  

```{r results = 'hold'}
cat(paste('Time stamp:', Sys.time(), '\n\n'))
cat('Runtime \n')
proc.time()
cat('\n')
sessionInfo()
```