---
title: "Pilot experiment 1"
author: "Matt Jaquiery"
date: "08/05/2020"
output: html_document
---

[Script run `r Sys.time()`]

```{r, include=F}
knitr::opts_chunk$set(echo = F)
```

```{r, include=F}
# library(checkpoint)         # Ensure CRAN packages have the right versions
# checkpoint('2020-05-08')  # All packages will be loaded as they stood at this date
library(tidyverse)
library(ggridges)
library(ez)
library(BayesFactor)
library(papaja)

theme_set(theme_apa() + theme(
  panel.grid = element_blank(),
  legend.position = 'top',
  text = element_text(size = 16)
))

#' Compare models within a anovaBF output to get relative likelihood
#' @param x the BFBayesFactor object containing the results
#' @param comparisons list of pairs of values for the comparisons. Values can be row numbers or model strings.
#' @return data frame with columns M1, M2, BF(M1,M2)
marginalBF <- function(x, comparisons) {
  ns <- rownames(x@bayesFactor)
  getIndex <- function(i) if (i %in% ns) which(ns == i) else i
  bf <- function(a, b) exp(a - b)
  out <- NULL
  for (comp in comparisons) {
    if (length(comp) == 1) {
      a <- getIndex(comp[1])
      out <- rbind(out, data.frame(
        M1 = ns[a],
        M2 = x@denominator@longName,
        BF.M1.M2 = exp(x@bayesFactor$bf[a])
      ))
    } else {
      a <- getIndex(comp[1]); b <- getIndex(comp[2]);
      out <- rbind(out, data.frame(
        M1 = ns[a], 
        M2 = ns[b],
        BF.M1.M2 = bf(x@bayesFactor$bf[a], x@bayesFactor$bf[b])
      ))
    }
    
  }
  if (!is.null(names(comparisons)))
    rownames(out) <- names(comparisons)
  out
}
```

# Introduction

How we judge our responsibility and the responsibility of others for actions’ outcomes has important consequences in our society. 
It is tightly related to whether we get rewarded or blamed for the actions we make, which is crucial for the maintenance of a cooperative and fair society. 
Even in our everyday lives, correctly or wrongfully attributing responsibility to ourselves and others for seemingly non crucial actions, can have emotional and long-term consequences.

How people attribute responsibility to themselves in a group is subjective: They tend to attribute higher responsibility for positive as compared to negative outcomes. 
This is known as the self-serving bias, where people claim more credit for positive events, while they duck responsibility for negative events (Caine & Schlenker, 1979; Forsyth & Schlenker, 1977; Leary & Forsyth, 1987; Miller & Schlenker, 1985).
This bias however does not seem to be purely selfish: it also appears when people judge their group or another person’s responsibility (Palmeira et al., 2015; Taylor & Doria, 1981). 
For example, in the context of advising, people exhibit an ‘other-serving’ bias as they tend to credit more than blame an advisor (Palmeira et al., 2015). 

In individual contexts, the rewards naturally seem to belong to the person producing a positive or negative outcome. 
In a group decision however, the outcome may be shared or given to one group member. 
It has been established that responsibility underlies ownership: control and intent of an action, which are directly associated with responsibility attributions, also predict whether a person is perceived as the owner of an object (Palamar et al., 2012). 
If attributions of responsibility predict ownership, is the opposite true?
Here we would like to address 1) whether _Outcome ownership_ changes attributions of responsibility and 2) whether _Outcome ownership_ is necessary for the self-serving and/or other-serving bias to appear.  
We investigate this question in a group decision-making context, where only one member can receive the outcome in each round. 

Participants will perform an online task where they make collective decisions through majority votes, then one member of the group can receive either a _Reward_ or _No reward_. 
Finally they will rate the responsibility of the group members for the outcome. 
This paradigm will allow us to address both questions stated above: 

1. by investigating whether responsibility attribution increases for the _Outcome owner_, although the control over the outcome is exactly similar. 

2. By checking whether the self and other-serving bias of higher responsibility ratings for positive outcomes depend on _Outcome ownership_. 

In other words, we will answer the question: do people exhibit the same self-serving bias when judging the responsibility for an outcome that is attributed to another member of their group? 
Do they also still exhibit an ‘other-serving’ bias when judging the responsibility of another group member who did not receive the outcome?
We will also investigate (1b) whether self- and other-serving biases are of similar strength.[^1b]

[^1b]:
  This is not investigated in Pilot 1 because all responsibility ratings are given for the participant themselves.

The study reported here is the first pilot study.
In this study, participants provided a rating of their own responsibility for the outcome on every trial.
For consistency with other studies in this series, we describe it as having a 2x2x2x1 factor structure, with all factors within-subjects:

* Whether the rated player is the _Outcome recipient_:  
    * _Outcome owner_ versus _Not outcome owner_  
* The _Outcome valence_:  
    * _Reward_ versus _No reward_  
* The _Vote status_ of the participant in the group decision process:  
    * _Participant in majority_ versus _Participant in minority_  
* Whether the _Responsibility judgement_ is made about:  
    * _Own responsibility_ versus _Another's responsibility_  
    * In this experiment all _Responsibility judgements_ are made about the participant's _Own responsibility_  

# Method

## Statistical analysis

The primary analysis technique is ANOVA (Bayesian and frequentist). 
Bayesian ANOVA results are obtained by taking the likelihood of a model with the effect of interest plus all simpler effects compared to an alternative containing only the simpler effects. 
For main effects, this is the model for the effect alone compared to the intercept-only model; for one-way interactions this is the main effects plus interaction-of-interest model compared to the main effects only model.

## Materials

Experiments were custom-written in HTML/CSS/JavaScript using the [jsPsych framework](https://www.jspsych.org/) and undertaken by participants over the internet using their own devices.
The experiment code was written by Marwa El Zein.

## Procedure

The entry point to the study is through recruitment on the Prolific (https://prolific.ac/) participant recruitment platform.
Participants accepting the study are forwarded to the experiment website, where they provide informed consent for participation before entering the main experiment page.
The experiment begins with detailed instruction pages which describe the structure of each round in the game, with screenshots of each stage, followed by a short training trial sequence.
Once they have read the instructions and familiarised themselves with the game, participants begin the main experiment, which consists of 3 blocks of 20 trials.
The 20 trials are a randomised sequence of balanced repetitions of each of the 8 unique trial types (as defined by whether the outcome is a reward/no reward; whether the participant is in the majority/minority; and whether the participant receives the outcome).
The a reward/no reward trials and the trials with the participant in the majority/minority occurred equally frequently, while the participant received the outcome on 40% of all trials (because we wanted to maximise this variation but felt that 50% of trials might be noticeably unrealistic with four other players in the game).

Each trial begins with a display of the five players.
This is followed by a screen in which the participant selects one of two gamble images.
Gamble images are selected from a collection of hand-drawn images of gambling devices and paraphernalia, and are counterbalanced such that each pair of images is shown the same number of times.
Which gamble is selected has no influence on the outcome of the trial, which is predetermined.
Once the participant selects a gamble the other option vanishes.

If the participant has not selected a gamble by the end of the choice window, the rest of the trial is cancelled and the participant is shown a warning message which states that they have failed to make a choice in time.
If the participant did select a gamble, the next screen indicates which gamble has been selected through the majority vote of all five players.
Next, the gamble is allocated to one of the players and its outcome is shown (a coin for a rewarded trial or a coin with a cross through it for an unrewarded trial).

Finally, the participant is asked to rate their own responsibility for the outcome using a slider.
The responsibility rating phase lasts until the responsibility ratings has been submitted.

Once all 60 experimental trials have been completed, participants are debriefed, thanked, and returned to Prolific.
Payment follows once all participants have completed the study and bonuses have been calculated.

## Open science

### Preregistration

Experiment 1 was not preregistered due to a technical glitch with the Open Science Framework platform (OSF).
The preregistration form was submitted, but it was never processed and added to the repository.

### Open materials

Materials for the studies can be found on the [GitHub repository](https://github.com/mjaquiery/responsibility-by-reward/tree/d6e65c5f4b62becfa23054c8e124d8916382b446/ATTRRESP) as it stood on 4th May 2020.

### Open data

We are happy to share the experimental data for these pilot studies, but may not upload them to a repository unless requested. 
Data for the main experiments will available online.

# Results

## Descriptive statistics

```{r read data}

suppressWarnings({
  x <- read.csv('../data/data50part.csv', stringsAsFactors = F) %>% 
    mutate_at(vars(c(trialnum, outcome)), as.numeric)
  y <- read.csv('../data/dataextra.csv', stringsAsFactors = F)
})

d <- bind_rows(x, y) %>% filter(label == 'scaleresp') %>% as_tibble()

```

### Exclusions

```{r exclusions, results = 'asis'}

d.old <- d

max_missed_trials <- 10
expected_trial_n <- 60

# double_entry
exclude_ids <- d %>%
  nest(d = -prolificid) %>%
  mutate(
    d = map(d, ~ filter(., subject_id != subject_id[1]))
  ) %>%
  unnest(cols = d) %>%
  select(subject_id) %>% 
  unique() %>%
  mutate(double_entry = T)

# max_missed_trials
exclude_ids <- full_join(
  exclude_ids,
  d %>% 
    nest(df = -subject_id) %>%
    mutate(missed_trials = 
             map_dbl(df, . %>% filter(is.na(rt), is.na(response), is.na(rtchoice), is.na(buttonchoice)) %>% nrow()),
           missed_trials = missed_trials >= max_missed_trials) %>%
    filter(missed_trials) %>%
    select(-df),
  by = "subject_id"
)

# expected_trial_n
exclude_ids <- full_join(
  exclude_ids, 
  d %>%
    nest(df = -subject_id) %>%
    mutate(df = map_dbl(df, nrow)) %>%
    filter(df < expected_trial_n) %>%
    mutate(trial_count = T) %>%
    select(-df),
  by = "subject_id"
  )

# We now remove missed trials
# Whether we do this BEFORE or AFTER checking consecutive responses matters
d <- d %>% filter(!is.na(rt), !is.na(response), !is.na(rtchoice), !is.na(buttonchoice))

# max_consec_resp
exclude_ids <- full_join(
  exclude_ids,
  d %>% 
    nest(d = c(-subject_id, -bloc)) %>%
    mutate(
      consec_resp = map_lgl(d, ~ all(.$buttonchoice == .$buttonchoice[1]))
    ) %>%
    filter(consec_resp) %>%
    select(subject_id, consec_resp) %>%
    unique(),
  by = "subject_id"
)

exclude_ids %>% 
  mutate(total_unique_exclusions = 1) %>% 
  select(everything(), total_unique_exclusions, -subject_id) %>% 
  summarise_all(sum, na.rm = T) %>% 
  pivot_longer(cols = everything(), 
               names_to = 'Reason', 
               values_to = 'N excluded') %>%
  apa_table()

d <- d %>% 
  filter(!(subject_id %in% exclude_ids$subject_id)) %>% 
  mutate(
    subject_id = factor(subject_id),
    status = factor(status, labels = c('Participant in majority', 
                                       'Participant in minority')),
    outcome = factor(outcome, labels = c('Reward', 'No reward')),
    getsout = factor(getsout, labels = c('Outcome owner', 'Not outcome owner'))
  )

```

Before exclusion we have `r length(unique(d.old$subject_id))` subject_ids. We now exclude participants who have more than `r max_missed_trials` missed trials, picked the gamble option on the same side for all the trials in a block (after removing incomplete responses),[^consec_resp] or fewer than `r expected_trial_n` trials recorded. Our final participant list contains `r length(unique(d$subject_id))` participants.

[^consec_resp]: 
  _Note_: The criterion for exclusion of participants for consecutive responses was preregistered as 10 consecutive trials with the same gamble response key. 
  It was not clear in our preregistration planning whether trials with no response should break up consecutive responses for this purpose.
  After determining that the particular implementation of this exclusion rule did not change the interpretations drawn from the analysis results and that consecutive gamble choice did not seem to be a marker of inattention, we instead adopted the simpler rule that all participants must have used both gamble choice response keys in every block of trials.

### Demographics 

```{r participant demographics, results = 'asis'}

d %>% 
  group_by(subject_id) %>%
  transmute(gender = str_to_upper(gender)) %>% 
  unique() %>%
  group_by(gender) %>%
  summarise(n = n(), .groups = 'drop') %>%
  apa_table()

gender <- d %>% 
  select(prolificid, gender) %>% 
  mutate(gender = str_to_upper(gender)) %>% 
  unique()

age <- d %>% 
  select(prolificid, age) %>% 
  unique()
```

Participants self-reported a mean age of `r pull(age, age) %>% mean() %>% round(1)` (SD = `r pull(age, age) %>% sd() %>% round(1)`) years and their genders as M (`r gender %>% filter(gender == 'M') %>% nrow()`), F (`r gender %>% filter(gender == 'F') %>% nrow()`), or otherwise (`r gender %>% filter(gender != 'M' & gender != 'F') %>% nrow()`).

Data were collected on the following days:

```{r experiment dates, results = 'asis'}
d %>%
  select(subject_id, date) %>%
  unique() %>%
  group_by(date) %>%
  summarise(n = n(), .groups = 'drop') %>%
  rename(Date = date, Participants = n) %>%
  apa_table()

```

### Response times

```{r}
max_rt <- 15000
```

Participants make two responses on a trial, choosing a gamble and indicating their feeling of responsibility. 
The distributions of the timings of these events for each participant are shown below for the first 15 seconds of the trials.
The `r sum(d$rtchoice > max_rt | d$rt > max_rt, na.rm = T)` responses which took longer than 15 seconds have been removed from this plot (the number for each participant is indicated in grey text), but remain in the responsibility rating data analysed in the main analysis.

```{r response time visualisations, fig.height=14, fig.width=6}

tmp <- d %>% 
  select(subject_id, rt, rtchoice) %>%
  pivot_longer(c(rt, rtchoice),
               names_to = "Event", 
               values_to = "Time") %>%
  mutate(subject_id = factor(subject_id),
         Event = case_when(Event == "rtchoice" ~ 'Gamble choice',
                           Event == "rt" ~ 'Responsibility rating',
                           T ~ NA_character_)) %>%
  filter(!is.na(Event) & !is.na(Time)) %>%
  rename(Participant = subject_id)

# Replace out-of-scale values with a count of dropped values
dropped <- tmp %>%
  # nest(n = -Participant) %>%
  # mutate(n = map_dbl(n, ~ filter(., Time > max_rt) %>% nrow()))
  group_by(Participant) %>%
  filter(Time > max_rt) %>%
  transmute(n = n())

tmp <- tmp %>% filter(Time <= max_rt)

ggplot(tmp, aes(y = Participant, x = Time, fill = Event, colour = Event)) +
  geom_vline(xintercept = 2000, linetype = 'dashed', colour = 'grey75') +
  geom_density_ridges(alpha = .25) +
  geom_point(position = position_jitter(0, .05), alpha = .25) +
  geom_text(aes(label = paste0('... +', dropped$n), y = Participant),
            inherit.aes = F, x = max_rt, colour = 'grey', data = dropped) +
  scale_x_continuous(limits = c(0, max_rt)) +
  labs(x = 'Time since trial start') +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = 'top'
  ) 

```

### Feeling of responsibility scale usage

This plot shows each participant's use of the responsibility rating scale, i.e. their answers to the question of how responsible they felt on each trial.

```{r feeling of responsibility visualisations, fig.height=24, fig.width=6}

tmp <- d %>%
  mutate(`Trial type` = paste0(
    if_else(status == 'Participant in majority', 'Majority', 'Minority'), ' - ',
    if_else(getsout == 'Outcome owner', 'gets outcome', 'does not get outcome'), ' ',
    if_else(outcome == 'Reward', '(reward)', '(no reward)')
  ),
    `Trial type` = factor(`Trial type`)) %>%
  select(subject_id, response, `Trial type`) %>%
  filter(!is.na(response)) %>%
  nest(df = -subject_id) %>%
  mutate(sum = map_dbl(df, ~ sum(.$response))) %>%
  unnest(cols = df)

tmp$subject_id <- reorder(tmp$subject_id, tmp$sum)

ggplot(tmp, aes(x = response, y = factor(subject_id), colour = `Trial type`, fill = `Trial type`)) +
  geom_density_ridges(alpha = .15) +
  scale_x_continuous(limits = c(0, 100)) +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    # legend.position = 'right',
    legend.direction = 'vertical'
  ) +
  labs(x = 'Own responsibility rating', y = 'Participant')

```

## Inferential statistics

```{r data preprocessing}
prettify <- function(d)
  d %>%
  mutate(`Outcome recipient` = getsout,
         `Outcome valence` = outcome,
         `Vote status` = status)

#' GGplot2 helper function to get offset x coordinates to the left or right
#' depending on whether the x coordinate is to the left or right.
#' @param x vector of x coordinates (typically factors)
#' @param amount amount to nudge in the appropriate direction
#' @param direction to nudge. 'outwards' is towards the extremes, 'inwards' is towards the centre.
nudge <- function(x, amount, direction = 'outwards') {
  if (!is.factor(x))
    x <- factor(x)
  x <- as.numeric(x) 
  dir <- if (direction == 'outwards') 1 else -1
  x + sign(x - mean(range(x, na.rm = T))) * dir * amount
}

```

### 1) Do participants feel more responsible if they are the _Outcome owner_?

```{r effect of getting the outcome}
dw <- .075

tmp <- d %>% 
  prettify() %>%
  group_by(subject_id, `Outcome recipient`) %>%
  filter(!is.na(response)) %>%
  summarise(response = mean(response), .groups = 'drop') 

bf <- ttestBF(
  x = tmp$response[tmp$`Outcome recipient` == 'Not outcome owner'],
  y = tmp$response[tmp$`Outcome recipient` != 'Not outcome owner'],
  paired = T
)

bf <- exp(bf@bayesFactor$bf) %>% round(2)

ggplot(tmp, aes(x = `Outcome recipient`, y = response)) +
  geom_line(aes(group = subject_id), colour = 'grey') +
  geom_boxplot(outlier.colour = NA, width = dw,
               aes(x = nudge(`Outcome recipient`, dw),
                   group = `Outcome recipient`)) +
  geom_segment(x = 1 - dw, xend = 2 + dw, y = 101, yend = 101) +
  geom_label(x = 1.5, y = 101, label = paste0('BF = ', bf)) +
  scale_x_discrete(expand = c(0, dw * 4)) +
  scale_y_continuous(limits = c(0, 100)) +
  labs(y = 'Rating of own responsibility')

```
The figure shows participant mean self-responsibility ratings collapsed across other trial factors (lines) and their distributions (box plots).
Participants rate their own responsibility as higher when they (rather than another participant) receive the outcome.

### 2) Does the self-serving bias, i.e, higher responsibility for positive _Outcome valence_, change if the participant is _Not outcome owner_?

```{r interaction of outcome valence and getting the outcome}

tmp <- d %>% 
  prettify() %>%
  group_by(subject_id, `Outcome recipient`, `Outcome valence`) %>%
  filter(!is.na(response)) %>%
  summarise(response = mean(response), .groups = 'drop')

bf <- tmp %>%
  nest(d = -`Outcome recipient`) %>%
  mutate(
    bf = map(d, ~ ttestBF(
      x = .$response[.$`Outcome valence` == 'No reward'],
      y = .$response[.$`Outcome valence` != 'No reward'],
      paired = T
    )),
    bf = map_dbl(bf, ~ .@bayesFactor %>% .$bf %>% exp() %>% round(2))
  ) %>%
  select(-d)

ggplot(tmp, aes(x = `Outcome valence`, y = response)) +
  geom_line(aes(group = subject_id), colour = "grey") +
  geom_boxplot(outlier.colour = NA, width = dw,
               aes(x = nudge(`Outcome valence`, dw),
                   group = `Outcome valence`)) +
  geom_segment(x = 1 - dw, xend = 2 + dw, y = 101, yend = 101) +
  geom_label(aes(label = paste0('BF = ', bf)), x = 1.5, y = 101, data = bf) +
  scale_x_discrete(expand = c(0, dw * 4)) +
  scale_y_continuous(limits = c(0, 100)) +
  labs(y = 'Rating of own responsibility') +
  facet_wrap(~paste0('When ', `Outcome recipient`))

```

The figure shows participant mean self-responsibility ratings collapsed across other trial factors (lines) and their distributions (box plots).
The effect of 'self-serving bias' is much clearer on trials where the participant gets the outcome than on trials where another player gets the outcome. 


We explored this statistically with a 2x2x2 ANOVA in which we saw an interaction between the effects of whether the participant receives the outcome ('getsout') and whether the outcome was good ('outcome'). 

```{r feeling of responsibility plot}
dw <- .25

d %>%
  prettify() %>%
  group_by(subject_id, `Vote status`, `Outcome valence`, `Outcome recipient`) %>% 
  filter(!is.na(response)) %>%
  summarise(response = mean(response), .groups = 'drop') %>%
  ggplot(aes(x = `Outcome valence`, 
             y = response, 
             colour = paste0('When ', `Outcome recipient`))) +
  geom_hline(yintercept = 20, linetype = 'dashed') +
  geom_point(alpha = .1, position = position_jitterdodge(dw/1.5, dodge.width = dw)) +
  stat_summary(geom = "point", aes(group = `Outcome recipient`), size = 4, 
               fun = mean, position = position_dodge(dw), shape = 0) +
  stat_summary(geom = "errorbar", aes(group = `Outcome recipient`), width = 0, 
               fun.data = mean_cl_normal, position = position_dodge(dw)) +
  stat_summary(geom = 'line', fun = mean, aes(group = `Outcome recipient`),
               position = position_dodge(dw)) +
  facet_wrap(~`Vote status`) +
  scale_colour_discrete(name = '') +
  labs(y = "Rating of own responsibility")

```

The figure shows participant mean self-responsibility ratings collapsed in each trial type (coloured dots). Squares indicate the mean for a trial type across all participant means, with the error bars giving 95% confidence intervals.

```{r ANOVA results, results = 'asis'}

suppressWarnings({
  a <- ezANOVA(
    data = d,
    dv = response,
    wid = subject_id,
    within = c(
      outcome,
      getsout,
      status
    )
  )
})


a %>%
  apa_table()

```

```{r Bayesian ANOVA results, results = 'asis'}

a.bf = anovaBF(
  data = as.data.frame(d),
  formula = response ~ 
    status + outcome + getsout + subject_id,
  whichRandom = 'subject_id', progress = F
)

a.bf %>% 
  marginalBF(comparisons = list(
    # 1, 2, 5, # Main effect vs random effects model
    c(8, 6), c(8, 3), c(8, 7), # Main effects vs model with other main effects
    c(14, 8), c(9, 8), c(11, 8), # 2-way interactions vs main effects model
    c(18, 17) # 3-way interactions vs 2-way interactions model
  )) %>%
  mutate(` ` = case_when(BF.M1.M2 < 1/3 ~ '-', 
                                   BF.M1.M2 > 3 ~ '+', 
                                   T ~ '')) %>%
  apa_table()

```

Participants showed a strong tendency to provide higher ratings for _Reward_ versus _No reward_ outcome valance ($F$(1, 53) = 28.46, $p$ < .001, $\eta_p^2$ = .030) and if they rather than another participant were the _Outcome owner_ ($F$(1, 53) = 15.48, $p$ < .001, $\eta_p^2$ = .017). 
There was no main effect of whether or not the Vote status put the _Participant in Majority_ ($\text{BF}_{10}$ = 1/25.09).
Moreover, the increase in ratings for _Rewarded_ vs _No reward_ trials was greater where the participant was the _Outcome owner_ ($F$(1, 53) = 9.46, $p$ < .001, $\eta_p^2$ = .005) or where the Vote status had the _Participant in Majority_ ($F$(1, 53) = 5.29, $p$ = .025, $\eta_p^2$ = .012). 
The increase in ratings of responsibility for trials on which participant was the _Outcome owner_ was equivalent whether or not the Vote status had the _Participant in Majority_ ($\text{BF}_{10}$ = 1/16.81).
Finally, there was a three-way interaction: the difference in responsibility for _Reward_ vs _No reward_ trials according to whether the participant was the _Outcome owner_ differed according to the Vote status ($F$(1, 53) = 7.64, $p$ = .001, $\eta_p^2$ = .003), although this was not confirmed by the Bayesian statistics because the result was uninformative (BF = 1.55).

# Interpretation

Pilot experiment 1 suggested that participants' feelings of responsibility were increased where the participant received the outcome of the chosen gamble (whether or not the outcome was a reward). 
This increase was greater where the outcome was a reward rather than no reward.

# References

Bruce T. Caine  and  Barry  R.  Schlenker. Role  Position and  Group  Performance  as  Determinants  of  Egotistical  Perceptions  in  Cooperative  Groups. The  Journal of  Psychology,   101(2):149–156,   March  1979. ISSN0022-3980. doi: 10.1080/00223980.1979.9915066. URL https://doi.org/10.1080/00223980.1979.9915066.

John  M.  Darley  and  Bibb  Latane.  Bystander  intervention in emergencies:  Diffusion of responsibility. Journal of Personality and Social Psychology, 8(4, Pt.1):377–383,1968. ISSN  1939-1315(Electronic), 0022-3514(Print). doi: 10.1037/h0025589.

Donelson R. Forsyth, Linda E. Zyzniewski, and Cheryl A. Giammanco. Responsibility   Diffusion   in   Cooperative   Collectives. Personality   and   Social   PsychologyBulletin,   28(1):54–65,   January   2002. ISSN   0146-1672. doi:10.1177/0146167202281005.URL https://doi.org/10.1177/0146167202281005.

Donelson   R.   Forsyth   and   Barry   R.   Schlenker. Attributing  the  causes  of  group  performance:   Effects  of performance  quality,  task  importance,  and  future  testing. Journal   of   Personality,   45(2):220–236,   1977. ISSN   1467-6494(Electronic), 0022-3506(Print). doi:10.1111/j.1467-6494.1977.tb00148.x.

Mark R. Leary and Donelson R. Forsyth.   Attributions of responsibility for collective endeavors. In Group processes, Review of personality and social psychology, Vol. 8., pages167–188. Sage Publications, Inc, Thousand Oaks, CA, US,1987. ISBN 978-0-8039-3071-1 978-0-8039-3072-8.

Rowland   S.   Miller   and   Barry   R.   Schlenker. Egotism   in   Group   Members: Public   and   Private   Attributions    of    Responsibility    for    Group    Performance. Social Psychology Quarterly, 48(1):85–89,1985. ISSN   0190-2725.doi:10.2307/3033785. URL https://www.jstor.org/stable/3033785.

Mauricio   Palmeira,    Gerri   Spassova,    and   Hean   TatKeh. Other-serving   bias   in   advice-taking: When advisors   receive   more   credit   than   blame. Organizational Behavior and Human Decision Processes,   130:13–25,   September   2015. ISSN   0749-5978.doi:10.1016/j.obhdp.2015.06.001. URL http://www.sciencedirect.com/science/article/pii/S0749597815000692.

Max  Rollwage,  Franziska  Pannach,  Caedyn  Stinson,  Ulf Toelch, Igor Kagan, and Arezoo Pooresmaeili.  Judgments of effort exerted by others are influenced by received rewards. Scientific Reports, 10(1):1–14, February 2020. ISSN 2045-2322.    doi:   10.1038/s41598-020-58686-0.    URLhttps://www.nature.com/articles/s41598-020-58686-0.

Donald  M.  Taylor  and  Janet  R.  Doria. Self-Serving and  Group-Serving  Bias  in  Attribution. The  Journal  of Social  Psychology,  113(2):201–211,  April  1981. ISSN0022-4545. doi: 10.1080/00224545.1981.9924371. URL https://doi.org/10.1080/00224545.1981.9924371. Publisher: Routledge_eprint: https://doi.org/10.1080/00224545.1981.9924371.


# Credits 

<!-- ## Acknowledgements -->

## R Packages

```{r R packages, results = 'asis'}
# list packages
packageNames <- (.packages())
# don't include very core package
packageNames <- packageNames[!(packageNames %in% 
                                 rownames(installed.packages(
                                   priority = "base")))]
# but do include the base package
packageNames <- c("base", packageNames)
out <- NULL
for (p in packageNames) {
  out <- rbind(out, data.frame('Package' = p, 
                               'Citations' = paste(format(citation(p), 
                                                          style = 'textVersion'), 
                                                   collapse = '<br/><br/>')))
}

out %>% apa_table()
```

## Funding

Marwa El Zein is a Sir Henry Wellcome Postdoctoral Fellow at University College London, funded by The Wellcome Trust.

Matt Jaquiery is funded by a studentship from the [Medical Research Council](https://mrc.ukri.org/) (reference 1943590) and the University of Oxford [Department of Experimental Psychology](https://www.psy.ox.ac.uk/) (reference 17/18_MSD_661552).

<hr/>

## Technical details  

```{r technical details, results = 'hold'}
cat(paste('Time stamp:', Sys.time(), '\n\n'))
cat('Runtime \n')
proc.time()
cat('\n')
sessionInfo()
```