---
title: "Main Experiment Analysis"
author: "Matt Jaquiery"
date: "16/11/2020"
output: html_document
---

[Script run `r Sys.time()`]

```{r, include=F}
knitr::opts_chunk$set(echo = F)
```

```{r, include=F}
library(tidyverse)
library(glue)
library(lubridate)
library(ggridges)
library(ez)
library(BayesFactor)
# library(papaja)

theme_set( 
  theme_light() #+
    # theme_apa() +
    # theme(
    #   panel.grid = element_blank(),
    #   legend.position = 'top',
    #   text = element_text(size = 16)
    # )
)

```

# Introduction



# Method

## Statistical analysis

The primary analysis technique is ANOVA (frequentist).

## Materials

Experiments were custom-written in HTML/CSS/JavaScript using the [jsPsych framework](https://www.jspsych.org/) and undertaken by participants over the internet using their own devices.
The experiment code was written by Marwa El Zein and Matt Jaquiery.

## Procedure

The entry point to the study is through recruitment on the Prolific (https://prolific.ac/) participant recruitment platform.
Participants accepting the study are forwarded to the experiment website, where they provide informed consent for participation before entering the main experiment page.
The experiment begins with detailed instruction pages which describe the structure of each round in the game, with screenshots of each stage, followed by a short training trial sequence.
Once they have read the instructions and familiarised themselves with the game, participants begin the main experiment, which consists of 3 blocks of 24 trials.
The 24 trials are a randomised sequence of balanced repetitions of each of the 12 unique trial types (as defined by whether the outcome is a reward/no reward; whether the participant is in the majority/minority; and which the player receives the outcome).
The a reward/no reward trials and the trials with the participant in the majority/minority occurred equally frequently, and each player receives the outcome on 1/3rd of all trials.
In trials where the participant is in the majority, one other player selects the same gamble as the participant and the other player selects a random gamble, meaning that on approximately half of these trials the vote is unanimous.

Each trial begins with a display of the three players.
This is followed by a screen in which the participant selects one of two gamble images.
Gamble images are selected from a collection of hand-drawn images of gambling devices and paraphernalia, and are counterbalanced such that each pair of images is shown the same number of times.
Which gamble is selected has no influence on the outcome of the trial, which is predetermined.
Once the participant selects a gamble the their player icon is shown on the gamble they chose.

If the participant has not selected a gamble by the end of the choice window, the rest of the trial is cancelled and the participant is shown a warning message which states that they have failed to make a choice in time.
If the participant did select a gamble, the player icons for the other players are shown on the gambles selected by the other players.
The gamble with two or more player icons is selected.
Next, the gamble is allocated to one of the players and its outcome is shown (a coin for a rewarded trial or a coin with a cross through it for an unrewarded trial).

Finally, the participant is asked to rate each player's responsibility for the outcome using a slider.
The responsibility rating phase lasts until all the responsibility ratings have been submitted.

Once all 72 experimental trials have been completed, participants are debriefed, thanked, and returned to Prolific.
Payment follows once all participants have completed the study and bonuses have been calculated.

## Open science

### Preregistration

This experiment is part of a registered report, and hence the analysis approach is preregistered in the Stage 1 submission (and the archive of this script on GitHub).

### Open materials

Materials for the studies can be found on the [GitHub repository](https://github.com/mjaquiery/responsibility-by-reward/ATTRRESP) as it stood on 16th November 2020.

### Open data

!TODO[Save data to repository, and load from the repository in the script below.]

```{r read data}

d <- read.csv('../data/finaldata.csv', sep = ",", stringsAsFactors = F) %>% 
  as_tibble() %>%
  bind_rows(
    read.csv('../data/finaldata2.csv', sep = ",", stringsAsFactors = F) %>%
      as_tibble()
  )

write.csv(d, '../data/main-data_raw.csv', row.names = F)

d

if (any(d$participant_id != 1, na.rm = T))
  stop("Some participants have the wrong id (should be 1). This must be corrected before this analysis will work correctly.")

```

### Exclusions

```{r descriptive stats}

d.old <- d

max_rating_time <- 15000 # 15s
max_missed_trials <- 10
expected_trial_n <- 72 # 3 sets of 2x12 trials
n_participants <- 500

# # double_entry -- taken care of by Prolific
# exclude_ids <- d %>%
#   nest(d = -prolificid) %>%
#   mutate(
#     d = map(d, ~ filter(., subject_id != subject_id[1]))
#   ) %>%
#   unnest(cols = d) %>%
#   select(subject_id) %>% 
#   unique() %>%
#   mutate(double_entry = T)
exclude_ids <- tribble(~ subject_id)

# mark trials that take too long as missed
d <- d %>% 
  mutate(tooLong = time_ratings_end - time_ratings_start > max_rating_time)

# max_missed_trials
exclude_ids <- full_join(
  exclude_ids,
  d %>% 
    nest(df = -subject_id) %>%
    mutate(missed_trials = 
             map_dbl(df, . %>% filter(vote_p1 == "" | tooLong) %>% nrow()),
           missed_trials = missed_trials >= max_missed_trials) %>%
    filter(missed_trials) %>%
    select(-df),
  by = "subject_id"
)

# expected_trial_n
exclude_ids <- full_join(
  exclude_ids, 
  d %>%
    filter(label == 'threePlayerGamble') %>%
    nest(df = -subject_id) %>%
    mutate(df = map_dbl(df, nrow)) %>%
    filter(df < expected_trial_n) %>%
    mutate(trial_count = T) %>%
    select(-df),
  by = "subject_id"
  )

# We now remove missed trials
# Whether we do this BEFORE or AFTER checking consecutive responses matters
d <- d %>% filter(vote_p1 != "" & !tooLong)

# max_consec_resp
exclude_ids <- full_join(
  exclude_ids,
  d %>% 
    nest(d = c(-subject_id, -block)) %>%
    mutate(
      consec_resp = map_lgl(d, ~ all(.$vote_p1 == .$vote_p1[1]))
    ) %>%
    filter(consec_resp) %>%
    select(subject_id, consec_resp) %>%
    unique(),
  by = "subject_id"
)

exclude_ids <- full_join(
  exclude_ids,
  d %>% 
    filter(!(subject_id %in% exclude_ids$subject_id)) %>%
    nest(d = -subject_id) %>%
    mutate(first = map_dbl(d, ~ min(as_datetime(.$date)))) %>%
    arrange(first) %>%
    rowid_to_column() %>%
    filter(rowid > n_participants) %>%
    transmute(subject_id, surplus_to_prereg = T),
  by = "subject_id"
)

exclude_ids %>% 
  mutate(total_unique_exclusions = 1) %>% 
  select(everything(), total_unique_exclusions, -subject_id) %>% 
  summarise_all(sum, na.rm = T) %>% 
  pivot_longer(cols = everything(), 
               names_to = 'Reason', 
               values_to = 'N excluded') 
  # apa_table()

d <- d %>% 
  filter(!(subject_id %in% exclude_ids$subject_id)) %>% 
  mutate(
    subject_id = factor(subject_id),
    status = factor(status, labels = c('Participant in majority', 
                                       'Participant in minority')),
    outcome = factor(outcome, labels = c('Reward', 'No reward')),
    getsout = factor(getsout, labels = c('Player 0', 'Participant', 'Player 2')),
    pgetsout = factor(if_else(getsout == "Participant", 1, 2), labels = c(
      'Participant gets outcome', 'Another gets outcome'
    ))
  )

```

Before exclusion we have `r length(unique(d.old$subject_id))` subject_ids. We now exclude participants who have more than `r max_missed_trials` missed or excessively slow trials, only used one of the two response keys in a block, or had fewer than `r expected_trial_n` trials recorded. 
Our final participant list contains `r length(unique(d$subject_id))` participants.

### Demographics 

```{r}

d %>% 
  transmute(unique_genders = str_to_upper(gender)) %>% 
  unique()

gender <- d %>% 
  select(subject_id, gender) %>% 
  mutate(gender = str_to_upper(gender)) %>% 
  unique()

age <- d %>% 
  select(subject_id, age) %>% 
  mutate(age = as.numeric(age)) %>%
  unique()

```

Participants self-reported a mean age of `r pull(age, age) %>% mean() %>% round(1)` (SD = `r pull(age, age) %>% sd() %>% round(1)`) years and their genders as M (`r gender %>% filter(gender == 'M') %>% nrow()`), F (`r gender %>% filter(gender == 'F') %>% nrow()`), or otherwise (`r gender %>% filter(gender != 'M' & gender != 'F') %>% nrow()`).

Data were collected on the following days:

```{r experiment dates, results = 'asis'}
d %>%
  transmute(subject_id, date = as_date(date)) %>%
  unique() %>%
  group_by(date) %>%
  summarise(n = n(), .groups = 'drop') %>%
  rename(Date = date, Participants = n) #%>%
  # apa_table()

```

### Response times

```{r}
max_rt <- 30000
```

Participants make four responses on a trial, choosing a gamble and indicating how responsible each of the players was for the decision. 

```{r response time visualisations, fig.height=14, fig.width=6}

tmp <- d %>% 
  select(subject_id, time_choice_start, time_choice_made, starts_with('responsibility_time')) %>%
  pivot_longer(c(time_choice_made, starts_with('responsibility_time')),
               names_to = "Event", 
               values_to = "Time") %>%
  mutate(Time = Time - time_choice_start) %>%
  mutate(Event = case_when(
    str_detect(Event, 'responsibility_time') ~ str_extract(Event, 'p[0-9]+$'),
    T ~ Event)
  ) %>%
  filter(!is.na(Event) & !is.na(Time)) %>%
  rename(Participant = subject_id)

# Replace out-of-scale values with a count of dropped values
dropped <- tmp %>%
  group_by(Participant) %>%
  filter(Time > max_rt) %>%
  transmute(n = n())

tmp <- tmp %>% filter(Time <= max_rt)

gg <- ggplot(tmp, aes(y = Participant, x = Time, fill = Event, colour = Event)) +
  geom_vline(xintercept = 2000, linetype = 'dashed', colour = 'grey75') +
  geom_density_ridges(alpha = .25) +
  geom_point(position = position_jitter(0, .05), alpha = .25)

if (nrow(dropped)) {
  gg <- gg + geom_text(
    aes(label = paste0('... +', n), y = Participant),
    inherit.aes = F, x = max_rt, colour = 'grey', data = dropped
  )  
}

gg + 
  scale_x_continuous(limits = c(0, max_rt)) +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = 'top'
  )

```


### Feeling of responsibility scale usage

```{r, fig.height=14, fig.width=6}

tmp <- d %>% 
  pivot_longer(starts_with('responsibility_rating_p'),
               names_to = 'rated_player',
               values_to = 'response') %>%
  mutate(rated_player = str_extract(rated_player, 'p[0-9]+$'),
         rated_player = if_else(rated_player == 'p1', 'Participant', rated_player)) %>%
  select(subject_id, response, rated_player) %>%
  nest(df = -subject_id) %>%
  mutate(sum = map_dbl(df, ~ sum(.$response))) %>%
  unnest(cols = df)
tmp$subject_id <- reorder(tmp$subject_id, tmp$sum)
  
ggplot(tmp, aes(x = response, y = factor(subject_id), 
                colour = rated_player, fill = rated_player)) +
  geom_density_ridges(alpha = .25) +
  scale_x_continuous(limits = c(0, 100)) +
  labs(y = 'Participant', x = 'Responsibility rating') +
  scale_colour_discrete(name = 'Rated player', aesthetics = c('colour', 'fill')) +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = 'top'
  ) 

```

## Main analysis

Participants make one rating of responsibility for each of the three players (including themself) on each trial. 
These data are averaged in order to conduct ANOVA by organising each rating on each trial according to the following factors:

* ANOVA:  
    * _Outcome valence_: Whether the trial result is _Reward_ or _No reward_  
    * _Outcome recipient_: Whether the rated player is the _Outcome owner_ or _Not outcome owner_  
    * _Is participant_: Whether the rated player is the _Participant_ or _Another player_   

```{r}

#' GGplot2 helper function to get offset x coordinates to the left or right
#' depending on whether the x coordinate is to the left or right.
#' @param x vector of x coordinates (typically factors)
#' @param amount amount to nudge in the appropriate direction
#' @param direction to nudge. 'outwards' is towards the extremes, 'inwards' is towards the centre.
nudge <- function(x, amount, direction = 'outwards') {
  if (!is.factor(x))
    x <- factor(x)
  x <- as.numeric(x) 
  dir <- if (direction == 'outwards') 1 else -1
  x + sign(x - mean(range(x, na.rm = T))) * dir * amount
}


d.long <- d %>% 
  pivot_longer(cols = starts_with('responsibility_rating_p'),
               names_to = 'rated_player',
               values_to = 'responsibility_rating') %>%
  mutate(rated_player = str_extract(rated_player, 'p[0-9]+$'),
         rated_player = case_when(rated_player == 'p0' ~ 'Player 0', 
                                  rated_player == 'p1' ~ 'Participant',
                                  rated_player == 'p2' ~ 'Player 2'),
         is_participant = factor(if_else(rated_player == 'Participant',
                                         'ratingForParticipant',
                                         'ratingForOther')),
         gout = if_else(getsout == 'Participant', 
                        'Participant', as.character(getsout)),
         rated_gets_outcome = str_detect(rated_player, paste0(gout)),
         rated_gets_outcome = factor(if_else(rated_gets_outcome, 
                                             'ratedGetsOutcome',
                                             'otherGetsOutcome')),
         `Outcome recipient` = if_else(
           rated_gets_outcome == "ratedGetsOutcome",
           "Outcome owner", "Not outcome owner"
         ),
         `Outcome valence` = outcome)

write.csv(d.long, '../data/main-data_processed.csv', row.names = F)

```

The main analysis is a 2x2x2 frequentist ANOVA.

```{r}

dw <- 1

d.long %>%
  group_by(subject_id, `Outcome valence`, `Outcome recipient`, is_participant) %>% 
  summarise(responsibility_rating = mean(responsibility_rating), .groups = 'drop') %>%
  mutate(
    `Is participant` = if_else(is_participant == "ratingForOther", "Other", "Self")
  ) %>%
  mutate(
    `Outcome recipient` = fct_rev(`Outcome recipient`),
    `Is participant` = fct_rev(`Is participant`)
  ) %>%
  ggplot(aes(x = `Is participant`, y = responsibility_rating, colour = `Outcome valence`)) +
  geom_hline(yintercept = 100 / 3, linetype = 'dashed') +
  geom_point(alpha = .1, position = position_jitterdodge(dw/3, dodge.width = dw)) +
  stat_summary(geom = "col", aes(group = `Outcome valence`), fill = NA, size = 1, 
               fun = mean, position = position_dodge(dw)) +
  stat_summary(geom = "errorbar", aes(group = `Outcome valence`), width = 0, 
               fun.data = mean_cl_normal, position = position_dodge(dw), size = 2.5) +
  scale_colour_discrete(h.start = 180) +
  scale_y_continuous(limits = c(0, 100), expand = c(0, 0)) +
  facet_wrap(~`Outcome recipient`) +
  labs(x = "", 
       y = "Participant rating of responsibility") +
  theme(
    legend.position = 'top',
    text = element_text(size = 20),
    panel.grid = element_blank()
  )

```

```{r}

suppressWarnings({
  a <- ezANOVA(
    data = d.long,
    dv = responsibility_rating,
    wid = subject_id,
    within = c(
      outcome,
      rated_gets_outcome,
      is_participant
    ),
    type = 3
  )
})

a # %>%
  # apa_table()

```

## Further inferential statistics

Below, we unfold the ANOVA results by responding to each of our research questions with a plot.
For interactions, we conduct additional post-hoc t-tests to better understand the interaction effects.

### 1) Are players considered more responsible if they are the _Outcome owner_?

```{r effect of getting the outcome}
dw <- .075

tmp <- d.long %>% 
  group_by(subject_id, `Outcome recipient`) %>%
  summarise(responsibility_rating = mean(responsibility_rating), .groups = 'drop') 

tt <- t.test(
  x = tmp$responsibility_rating[tmp$`Outcome recipient` == 'Not outcome owner'],
  y = tmp$responsibility_rating[tmp$`Outcome recipient` != 'Not outcome owner'],
  paired = T
)

tt <- glue("T({ tt$parameter }) = { round(tt$statistic, 2) }; p = { format(tt$p.value, scientific = T, digits = 2) }")

ggplot(tmp, aes(x = `Outcome recipient`, y = responsibility_rating)) +
  geom_line(aes(group = subject_id), colour = 'grey') +
  geom_boxplot(outlier.colour = NA, width = dw,
               aes(x = nudge(`Outcome recipient`, dw),
                   group = `Outcome recipient`)) +
  geom_segment(x = 1 - dw, xend = 2 + dw, y = 101, yend = 101) +
  geom_label(x = 1.5, y = 101, label = tt) +
  scale_x_discrete(expand = c(0, dw * 4)) +
  scale_y_continuous(limits = c(0, 100)) +
  labs(y = 'Rating of responsibility')

```

The figure shows participant mean responsibility ratings collapsed across other trial factors (lines) and their distributions (box plots).
Participants rate players' responsibility as higher when that player receives the outcome.

### 2) Does the self/other-serving bias, i.e, higher responsibility for positive _Outcome valence_, change if the rated player is _Not outcome owner_?

```{r interaction of outcome valence and getting the outcome}

tmp <- d.long %>% 
  group_by(subject_id, `Outcome recipient`, `Outcome valence`) %>%
  summarise(responsibility_rating = mean(responsibility_rating), 
            .groups = 'drop')

tt <- tmp %>%
  nest(d = -`Outcome recipient`) %>%
  mutate(
    tt = map(d, ~ t.test(
      x = .$responsibility_rating[.$`Outcome valence` == 'No reward'],
      y = .$responsibility_rating[.$`Outcome valence` != 'No reward'],
      paired = T
    )),
    tt = map_chr(tt, ~ glue("T({ .$parameter }) = { round(.$statistic, 2) }; p = { format(.$p.value, scientific = T, digits = 2) }"))
  ) %>%
  select(-d)

ggplot(tmp, aes(x = `Outcome valence`, y = responsibility_rating)) +
  geom_line(aes(group = subject_id), colour = "grey") +
  geom_boxplot(outlier.colour = NA, width = dw,
               aes(x = nudge(`Outcome valence`, dw),
                   group = `Outcome valence`)) +
  geom_segment(x = 1 - dw, xend = 2 + dw, y = 101, yend = 101) +
  geom_label(aes(label = tt), x = 1.5, y = 101, data = tt) +
  scale_x_discrete(expand = c(0, dw * 4)) +
  scale_y_continuous(limits = c(0, 100)) +
  labs(y = 'Rating of responsibility') +
  facet_wrap(~paste0('When ', `Outcome recipient`))

```

The figure shows participant mean responsibility ratings collapsed across other trial factors (lines) and their distributions (box plots).
The 'self/other-serving bias' is evident on trials where the rated player gets the outcome, but not where another player gets the outcome. 

# Interpretation

# References 

# Credits 

<!-- ## Acknowledgements -->

## R Packages

```{r R packages, results = 'asis'}
# list packages
packageNames <- (.packages())
# don't include very core package
packageNames <- packageNames[!(packageNames %in% 
                                 rownames(installed.packages(
                                   priority = "base")))]
# but do include the base package
packageNames <- c("base", packageNames)
out <- NULL
for (p in packageNames) {
  out <- rbind(out, data.frame('Package' = p, 
                               'Citations' = paste(format(citation(p), 
                                                          style = 'textVersion'), 
                                                   collapse = '<br/><br/>')))
}

out # %>% apa_table()
```

## Funding

Marwa El Zein is a Sir Henry Wellcome Postdoctoral Fellow at University College London, funded by The Wellcome Trust (grant number 204702).

Matt Jaquiery is funded by a studentship from the [Medical Research Council](https://mrc.ukri.org/) (reference 1943590) and the University of Oxford [Department of Experimental Psychology](https://www.psy.ox.ac.uk/) (reference 17/18_MSD_661552).

<hr/>

## Technical details  

```{r technical details, results = 'hold'}
cat(paste('Time stamp:', Sys.time(), '\n\n'))
cat('Runtime \n')
proc.time()
cat('\n')
sessionInfo()
```